Response to decision letter

### 2023-08-09 review2.Rmd
streamline fig 1

> I thank the authors for their extensive and careful revisions to the manuscript. It has been reviewed by Associate Editor Dr Daniele Silvestro and myself. We both agree that the manuscript has been greatly improved and meets all the previous requests of the referees and the AE. The AE has several other suggestions that you should find useful while preparing the revision, mainly concerning editorial and formatting issues. I agree that some of your figures are difficult to visualize, for example Figs. 1 and 4, where you could use less color and more simple lines (they resemble a poster). Figure 5 is too large and detailed: it could never be published as an A4. I also wonder if all figures are necessary: for example, Figures 5 and 6 could be moved to the Supplementary; there is no limit in the number of figures in Software papers but we typically publish 4 figures per paper. Please consider these recommendations as you revise the manuscript.

@@

@@

>>>>

> I thank the authors for their extensive and careful revisions to the manuscript. It has been reviewed by Associate Editor Dr Daniele Silvestro and myself. We both agree that the manuscript has been greatly improved and meets all the previous requests of the referees and the AE. The AE has several other suggestions that you should find useful while preparing the revision, mainly concerning editorial and formatting issues.

I agree that some of your figures are difficult to visualize, for example Figs. 1 and 4, where you could use less color and more simple lines (they resemble a poster).

@@

Figure 5 is too large and detailed: it could never be published as an A4. 
I also wonder if all figures are necessary: for example, Figures 5 and 6 could be moved to the Supplementary; there is no limit in the number of figures in Software papers but we typically publish 4 figures per paper. Please consider these recommendations as you revise the manuscript.

**We moved figures 5 and 6 to supplementary materials.**

@@

We streamlined the figure by removing text in the figure and adding it to the figure caption. We considered removing the tables, but we decided to keep them as they are important for the explanation of the workflow. We hope this new version of the figure is considerably clearer now.

### 2023-08-09 submission/final-captions.tex
streamline fig 1

Main DateLife workflow. Analyses can be performed via DateLife's interactive website at \url{www.datelife.org}, or using the \texttt{datelife} R package. Details on the R functions used to perform the analyses are available from \texttt{datelife}'s R package vignettes at \url{https://phylotastic.org/datelife}.

>>>>

Main DateLife workflow to obtain sceintific data of time of lineage divergence for a set of taxon names. a) The workflow starts with at least two taxon names provided by the user as a list or as tip names on a tree. Input names can contain synonyms and misspellings.
b) Taxon names are processed using the Taxonomic Name Resolution Service (TNRS) and are standardized to the taxonomy of the chronogram database. In this mock example, 4 names (in bold) are synonyms in the standardized taxonomy.
c) Processed taxon names are searched in the chronogram database. Chronograms that have at least two taxon names are identified (*), pruned down to matching taxon names only, and stored as source chronograms for the set of input taxon names.
d) A topology to map ages from source chronograms can be provided by the user. If no topology is provided, OpenTree's synthetic tree topology is used. Alternative topologies that can be used are the largest (with the most input taxon names) source chronogram or a phylogeny constructed using genetic data from the Barcode of Life Database (BOLD).
e) Nodes from source chronogram are congruified to nodes from the tree topology chosen in step (d). In this example all ages from source chronograms are congruent with nodes on the tree topology and provide time of divergenve information for all but one node (n2).
f) Source node ages per node are summarized.
g) Summary node ages are used as secondary calibrations to date the chosen tree topology. In this example we show the chronogram of median ages.
All this analyses can be performed via DateLife's interactive website at \url{www.datelife.org}, or using the \texttt{datelife} R package. Details on the R functions used to perform the analyses are available from \texttt{datelife}'s R package vignettes at \url{https://phylotastic.org/datelife}.
